# Command wrappers

```{bash}

srun -p cpu --time 4:00:00 --ntasks 1 --cpus-per-task 6 --mem 32G --pty /bin/bash

srun -p cpu --time 4:00:00 --ntasks 1 --cpus-per-task 6 --mem 256G --pty /bin/bash

srun -p cpu --time 4:00:00 --ntasks 1 --cpus-per-task 16 --mem 128G --pty /bin/bash

srun -p cpu --time 4:00:00 --ntasks 1 --cpus-per-task 16 --mem 128G --pty /bin/bash

srun -p interruptible_cpu --time 4:00:00 --ntasks 1 --cpus-per-task 16 --mem 128G --pty /bin/bash


```


# PGS feasibility check across fractions of multisampled HG002/sequencing depths

```{bash}

#convert to plink format for SBayesRC scoring
#run in wprk/pgs

printf "hg002-100\nhg002-75\nhg002-50\nhg002-25\nhg002-20\nhg002-15\nhg002-15\nhg002-10\nhg002-05\n" > hg002-multisample-sample-names.txt
#printf "hg002-100\nhg002-75\nhg002-50\nhg002-25\n" > hg002-multisample-sample-names.txt


bcftools merge --force-samples -o hg002-multisampled.bcf /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/test-2/wf-pgx/bed/hg002-100-p3/output/HG002_new_hg19_merged_hg38/HG002_new_hg19_merged_hg38.filtered.vcf.gz /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/test-2/wf-pgx/bed/hg002-75-p3/output/HG002_new_hg19_merged/HG002_new_hg19_merged.filtered.vcf.gz /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/test-2/wf-pgx/bed/hg002-50-p3/output/HG002_new_hg19_merged/HG002_new_hg19_merged.filtered.vcf.gz /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/test-2/wf-pgx/bed/hg002-25-p3/output/HG002_new_hg19_merged/HG002_new_hg19_merged.filtered.vcf.gz
/users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/test-2/wf-pgx/bed/hg002-20-p3/output/HG002_new_hg19_merged/HG002_new_hg19_merged.filtered.vcf.gz
/users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/test-2/wf-pgx/bed/hg002-15-p3/output/HG002_new_hg19_merged/HG002_new_hg19_merged.filtered.vcf.gz
/users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/test-2/wf-pgx/bed/hg002-10-p3/output/HG002_new_hg19_merged/HG002_new_hg19_merged.filtered.vcf.gz
/users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/test-2/wf-pgx/bed/hg002-05-p3/output/HG002_new_hg19_merged/HG002_new_hg19_merged.filtered.vcf.gz

#bcftools reheader -s hg002-multisample-sample-names.txt -o hg002-multisampled.vcf.gz hg002-multisampled.vcf.gz --this messes with teh file format somehow

bcftools view -H hg002-multisampled.bcf | head -n 250

tabix -p bcf hg002-multisampled.bcf

#this needs lots of memory?
sbatch --time 3:00:00 --partition cpu --job-name="annotate" --ntasks 1 --cpus-per-task 6 --mem 64G --wrap="bcftools annotate -a /scratch/prj/gwas_sumstats/reference_panel/hc1kgp3.b38.plink/hc1kgp3.b38.eur.jz2024.vcf.gz -o hg002-multisampled.vcf.gz hg002-multisampled.bcf" --output "prs.annotate.$(date +%Y%m%d).out.txt" 

bcftools annotate -a /scratch/prj/gwas_sumstats/reference_panel/hc1kgp3.b38.plink/hc1kgp3.b38.eur.jz2024.vcf.gz hg002-multisampled.bcf > hg002-multisampled.vcf


bcftools view -H hg002-multisampled.annotated.vcf.gz | head -n 1000
bcftools view -H hg002-multisampled.annotated.bcf | head -n 1000

plink --vcf hg002-multisampled.vcf.gz --out hg002-multisampled

sbatch --time 3:00:00 --partition cpu --job-name="sMDDIDP" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ~/project/prada_jz/manual_routines/prs-check-gladp-hg002-upsampling.R score MDDIDP" --output "prs.score.MDDIDP.$(date +%Y%m%d).out.txt"

sbatch --time 3:00:00 --partition cpu --job-name="sBIPO03" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ~/project/prada_jz/manual_routines/prs-check-gladp-hg002-upsampling.R score BIPO03" --output "prs.score.BIPO03.$(date +%Y%m%d).out.txt"

sbatch --time 3:00:00 --partition cpu --job-name="sBIPO03" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ~/project/prada_jz/manual_routines/prs-check-gladp-hg002-upsampling.R score BIPO03" --output "prs.score.BIPO03.$(date +%Y%m%d).out.txt"


```

# PGS feasibility check across region coverages

We measure the performance of PGS with the coverage of polygenic regions. We compare to the genome-wide case, using GLAD+ genotyped data.

```bash


sbatch --time 3:00:00 --partition cpu --job-name="munge" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R MDDIDP" --output "prs.munge.cojo.MDDIDP.$(date +%Y%m%d).out.txt"
sbatch --time 3:00:00 --partition cpu --job-name="munge" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R BIPO03" --output "prs.munge.cojo.BIPO03.$(date +%Y%m%d).out.txt"
sbatch --time 3:00:00 --partition cpu --job-name="munge" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R ADHD06" --output "prs.munge.cojo.ADHD06.$(date +%Y%m%d).out.txt"
sbatch --time 3:00:00 --partition cpu --job-name="munge" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R SCHI06" --output "prs.munge.cojo.SCHI06.$(date +%Y%m%d).out.txt"
sbatch --time 3:00:00 --partition cpu --job-name="munge" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R SMOK11" --output "prs.munge.cojo.SMOK11.$(date +%Y%m%d).out.txt"


sbatch --time 2-00:00:00 --partition cpu --job-name="MDDIDP" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R MDDIDP" --output "sbayesrc.tidyimpute.MDDIDP.$(date +%Y%m%d).out.txt"
sbatch --time 2-00:00:00 --partition cpu --job-name="BIPO03" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R BIPO03" --output "sbayesrc.tidyimpute.BIPO03.$(date +%Y%m%d).out.txt"
sbatch --time 2-00:00:00 --partition cpu --job-name="ADHD06" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R ADHD06" --output "sbayesrc.tidyimpute.ADHD06.$(date +%Y%m%d).out.txt"
sbatch --time 2-00:00:00 --partition cpu --job-name="SCHI06" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R SCHI06" --output "sbayesrc.tidyimpute.SCHI06.$(date +%Y%m%d).out.txt"
sbatch --time 2-00:00:00 --partition cpu --job-name="SMOK11" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R SMOK11" --output "sbayesrc.tidyimpute.SMOK11.$(date +%Y%m%d).out.txt"


sbatch --time 2-00:00:00 --partition cpu --job-name="MDDIDP" --ntasks 1 --cpus-per-task 8 --mem 32G --wrap="Rscript ../manual_routines/prs-check-gladp.R MDDIDP" --output "sbayesrc.score.MDDIDP.$(date +%Y%m%d).out.txt"
sbatch --time 2-00:00:00 --partition cpu --job-name="BIPO03" --ntasks 1 --cpus-per-task 8 --mem 32G --wrap="Rscript ../manual_routines/prs-check-gladp.R BIPO03" --output "sbayesrc.score.BIPO03.$(date +%Y%m%d).out.txt"
sbatch --time 2-00:00:00 --partition cpu --job-name="ADHD06" --ntasks 1 --cpus-per-task 8 --mem 32G --wrap="Rscript ../manual_routines/prs-check-gladp.R ADHD06" --output "sbayesrc.score.ADHD06.$(date +%Y%m%d).out.txt"
sbatch --time 2-00:00:00 --partition cpu --job-name="SCHI06" --ntasks 1 --cpus-per-task 8 --mem 32G --wrap="Rscript ../manual_routines/prs-check-gladp.R SCHI06" --output "sbayesrc.score.SCHI06.$(date +%Y%m%d).out.txt"
sbatch --time 2-00:00:00 --partition cpu --job-name="SMOK11" --ntasks 1 --cpus-per-task 8 --mem 32G --wrap="Rscript ../manual_routines/prs-check-gladp.R SMOK11" --output "sbayesrc.score.SMOK11.$(date +%Y%m%d).out.txt"


sbatch --time 4:00:00 --partition cpu --job-name="scoring" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R" --output "sbayesrc.scoring.baseline.$(date +%Y%m%d).out.txt"
#needs plink2
sbatch --time 4:00:00 --partition cpu --job-name="scoring" --ntasks 1 --cpus-per-task 6 --mem 16G --wrap="Rscript ../manual_routines/prs-check-gladp.R" --output "sbayesrc.scoring.allPolygenic.$(date +%Y%m%d).out.txt"

```

# ONT human variation workflow

## Installation and configuration

```bash

export JAVA_HOME='/scratch/prj/ppn_tng/software/java/jdk-24.0.1'
export JAVA_CMD='/scratch/prj/ppn_tng/software/java/jdk-24.0.1/bin/java'

export NEXTFLOW_CMD='/scratch/prj/ppn_tng/software/nextflow/nextflow-25.04.4-dist'

$NEXTFLOW_CMD pull epi2me-labs/wf-human-variation

$NEXTFLOW_CMD run epi2me-labs/wf-human-variation --help

```

# Singularity

Install singularity. Singularity can't build containers on MacOS currently. You can use a virtual machine (f.ex. using VirtualBox) to run Linux and then build Singularity that can build containers from definitions.
https://github.com/sylabs/singularity/blob/main/INSTALL.md
https://docs.sylabs.io/guides/3.0/user-guide/installation.html


Install prerequisites
```bash
sudo pacman -Syu
sudo pacman -Sy autoconf automake cryptsetup crun fuse2fs git fuse3 libseccomp libtool pkgconf shadow squashfs-tools wget zlib conmon go base-devel

#base-devel includes gcc and make

```

After restart, this is the rouine of the installation.
```bash
#in projects directory
git clone --recurse-submodules https://github.com/sylabs/singularity.git
cd singularity
#git submodule update --init #only if you don't already have the submodules
./mconfig
make -C builddir
sudo make -C builddir install

```


# Building a mosdepth container/image

```bash



#this was run historically - using a slimmed down version of mosdepth_c2.def to identify build errors
#sudo singularity build --sandbox mosdepth_c2 /media/sf_mylinux_shared/mosdepth_c2.def

sudo singularity build mosdepth_c2.sif /media/sf_mylinux_shared/mosdepth_c2.def
#singularity build --fakeroot mosdepth_c2.sif /media/sf_mylinux_shared/mosdepth_c2.def #this did not work

#test of using shared folder for cache and tempdir - THIS DOES NOT WORK CURRENTLY!
#if required - set the group permission for the user (q)
sudo usermod -aG vboxsf q
#sudo -E required in archlinux according to https://github.com/apptainer/singularity/issues/5791
#enable symlinks in the shared folder (virtualbox mylinux and share mylinux_shared)
VBoxManage setextradata mylinux VBoxInternal2/SharedFoldersEnableSymlinksCreate/mylinux_shared 1
export SINGULARITY_TMPDIR="/media/sf_mylinux_shared/singularity_tmp"
export SINGULARITY_CACHEDIR="/media/sf_mylinux_shared/singularity_cache"
sudo -E singularity build prada_c2.sif prada_c2.def #as root, in /media/sf_mylinux_shared/singularity_tmp
#singularity build --fakeroot prada_c2.sif prada_c2.def #does not work still

#clean environment
sudo pacman -Sc
sudo pacman -Scc
singularity cache clean

#running in larger vmachine
export SINGULARITY_TMPDIR="/home/q/Documents/work/sing_temp"
export SINGULARITY_CACHEDIR="/home/q/Documents/work/sing_cache"
sudo -E singularity build prada_c2.sif /media/sf_mylinux_shared/prada_c2.def
#this works. not sure if it is the change in disk or the use of -E.

```





#Creating IGV graphs


```bash

gunzip -c barcode01.regions.bed.gz | awk '{print $1, $2, $3, $5}' > barcode01.regions.bedgraph
gunzip -c barcode01.per-base.bed.gz | awk '{print $1, $2, $3, $4}' > barcode01.per-base.bedgraph

gunzip -c barcode02.regions.bed.gz | awk '{print $1, $2, $3, $5}' > barcode02.regions.bedgraph
gunzip -c barcode02.per-base.bed.gz | awk '{print $1, $2, $3, $4}' > barcode02.per-base.bedgraph

gunzip -c barcode03.regions.bed.gz | awk '{print $1, $2, $3, $5}' > barcode03.regions.bedgraph
gunzip -c barcode03.per-base.bed.gz | awk '{print $1, $2, $3, $4}' > barcode03.per-base.bedgraph

gunzip -c barcode04.regions.bed.gz | awk '{print $1, $2, $3, $5}' > barcode04.regions.bedgraph
gunzip -c barcode04.per-base.bed.gz | awk '{print $1, $2, $3, $4}' > barcode04.per-base.bedgraph

#interactive
#test of automated igvtools conversion to tdf
singularity shell --bind /scratch/prj/sgdp_nanopore/Projects/prada_jz /scratch/prj/sgdp_nanopore/Projects/prada_jz/venv/prada_c2.sif

igvtools toTDF /scratch/prj/sgdp_nanopore/Projects/prada_jz/work/mosdepth/pilot2/p2-nogtube-nobedtest/barcode01.regions.bedgraph barcode01.regions.tdf hg38 #this throws an error


```


#Analysing existing pilot runs on Create

Run in work/pradaApp

## Interactive version

```{R}
#remotes::install_github("tnggroup/prada")
#remotes::install_github("tnggroup/prada",ref = 'jz_dev')

library(prada)
library(data.table)

projectFolderPath<-"/scratch/prj/sgdp_nanopore/Projects/prada_jz"
pradaObj<-PradaClass()

pradaObj$addAnalysisSetting(settingLabel = "p2-gtube",folderPathAnalysisSequencingRaw = file.path(projectFolderPath, "data/ont_raw/pilot2/Gtube/20250724_1536_3B_PAW94949_16dd4442"),folderPathAnalysisOutputRaw = file.path(projectFolderPath, "work/pgx/pilot2/p2-gtube"),folderPathDepthAnalysisOutputRaw = file.path(projectFolderPath,"work/mosdepth/pilot2/p2-gtube"))
pradaObj$addAnalysisSetting(settingLabel = "p2-nogtube",folderPathAnalysisSequencingRaw = file.path(projectFolderPath,"data/ont_raw/pilot2/No_Gtube/20250724_1536_3C_PAY03690_092497cc"),folderPathAnalysisOutputRaw = file.path(projectFolderPath,"work/pgx/pilot2/p2-nogtube"),folderPathDepthAnalysisOutputRaw = file.path(projectFolderPath,"work/mosdepth/pilot2/p2-nogtube"))

pradaObj$addAnalysisSetting(settingLabel = "hg002-100",folderPathAnalysisSequencingRaw = NA,folderPathAnalysisOutputRaw = file.path(projectFolderPath,"work/pgx/downsampled-bam-runs/hg002-100"),folderPathDepthAnalysisOutputRaw = file.path(projectFolderPath,"work/mosdepth/downsampled-bam-runs/hg002-100"))

pradaObj$addAnalysisSetting(settingLabel = "hg002-75",folderPathAnalysisSequencingRaw = NA,folderPathAnalysisOutputRaw = file.path(projectFolderPath,"work/pgx/downsampled-bam-runs/hg002-75"),folderPathDepthAnalysisOutputRaw = file.path(projectFolderPath,"work/mosdepth/downsampled-bam-runs/hg002-75"))

pradaObj$addAnalysisSetting(settingLabel = "hg002-50",folderPathAnalysisSequencingRaw = NA,folderPathAnalysisOutputRaw = file.path(projectFolderPath,"work/pgx/downsampled-bam-runs/hg002-50"),folderPathDepthAnalysisOutputRaw = file.path(projectFolderPath,"work/mosdepth/downsampled-bam-runs/hg002-50"))

pradaObj$addAnalysisSetting(settingLabel = "hg002-25",folderPathAnalysisSequencingRaw = NA,folderPathAnalysisOutputRaw = file.path(projectFolderPath,"work/pgx/downsampled-bam-runs/hg002-25"),folderPathDepthAnalysisOutputRaw = file.path(projectFolderPath,"work/mosdepth/downsampled-bam-runs/hg002-25"))


#custom samples from hg002
pradaObj$addSampleSetting(analysis = "hg002-100",sampleLabel = "HG002_new")
pradaObj$addSampleSetting(analysis = "hg002-75",sampleLabel = "HG002_new")
pradaObj$addSampleSetting(analysis = "hg002-50",sampleLabel = "HG002_new")
pradaObj$addSampleSetting(analysis = "hg002-25",sampleLabel = "HG002_new")

pradaObj$collectAnalysisCallData("p2-gtube")
pradaObj$collectAnalysisCallData("p2-nogtube")
pradaObj$collectAnalysisCallData("hg002-100",addBarcodeParticipantsFromData = FALSE)
pradaObj$collectAnalysisCallData("hg002-75",addBarcodeParticipantsFromData = FALSE)
pradaObj$collectAnalysisCallData("hg002-50",addBarcodeParticipantsFromData = FALSE)
pradaObj$collectAnalysisCallData("hg002-25",addBarcodeParticipantsFromData = FALSE)


pradaObj$collectAnalysisDepthData("p2-gtube")
pradaObj$collectAnalysisDepthData("p2-nogtube")
pradaObj$collectAnalysisDepthData("hg002-100")
pradaObj$collectAnalysisDepthData("hg002-75")
pradaObj$collectAnalysisDepthData("hg002-50")
pradaObj$collectAnalysisDepthData("hg002-25")


pradaObj$computeDepthDataStatistics(filePathBed <- file.path(projectFolderPath,"data/bed/pgx_cnv.grch38.5k.2p1percent.bed"),filePathApplicationCoverageRegions = file.path(projectFolderPath,"data/applicationCoverageRegionsAsOfPilot2.tsv"))
pradaObj$computeCallStatistics(filePathApplicationCoverageRegions = file.path(projectFolderPath,"data/applicationCoverageRegionsAsOfPilot2.tsv"))
pradaObj$printData()


#plotTable<-as.data.frame(matrix(NA,0,0))

sampleMeta<-data.table::fread("sampleMeta.tsv")
sampleMeta[,sampleLabel:=paste0(analysis,"_",barcode)]

if(nrow(sampleMeta)>0){
      for(iSample in 1:nrow(sampleMeta)){
        #iSample<-1
        cAnalysisLabel<-sampleMeta[iSample,c("analysis")]
        cBarcode<-sampleMeta[iSample,c("barcode")]
        cUniqueSampleLabel <- paste0(cAnalysisLabel,"_",cBarcode)
        
        cStats<-data.table::fread(paste0("sequencingStatsOriginalRegionsTable_",cUniqueSampleLabel,".tsv"))
        cPgx<-data.table::fread(paste0("pgxCallsAggCustom_",cUniqueSampleLabel,".tsv"))
        cPgx[,pgxVariantRatio:=nvariants_mean/(nvariants_mean+nmissingpos_mean)]
        
        sampleMeta[sampleLabel==eval(cUniqueSampleLabel),c("nCalledPgx")]<-nrow(cPgx[!is.na(diplotype_score_top),])
        sampleMeta[sampleLabel==eval(cUniqueSampleLabel),c("meanPgxVariantRatio")]<-mean(cPgx$pgxVariantRatio,na.rm=T)
        
      }
        
}

library(ggplot2)

ggplot(sampleMeta,aes(x = sdepth_q050_bed, y = nvarq_region, colour = analysis)) + 
  geom_point() +
  theme_minimal()
#plot(sampleMeta$sdepth_q050_bed,sampleMeta$nvarq_region)

ggplot(sampleMeta,aes(x = sdepth_q050_bed, y = vcallacc_q050_region, colour = analysis)) + 
  geom_point() +
  theme_minimal()
#plot(sampleMeta$sdepth_q050_bed,sampleMeta$vcallacc_q050_region)

ggplot(sampleMeta,aes(x = sdepth_q050_bed, y = meanPgxVariantRatio, colour = analysis)) + 
  geom_point() +
  theme_minimal()
#plot(sampleMeta$sdepth_q050_bed,sampleMeta$meanPgxVariantRatio)

ggplot(sampleMeta,aes(x = sdepth_q050_bed, y = nCalledPgx, colour = analysis)) + 
  geom_point() +
  theme_minimal()
#plot(sampleMeta$sdepth_q050_bed,sampleMeta$nCalledPgx)


ggplot(sampleMeta,aes(x = sdepth_q050_nobed, y = nvarq_noregion, colour = analysis)) + 
  geom_point() +
  theme_minimal()

ggplot(sampleMeta,aes(x = sdepth_q050_nobed, y = vcallacc_q050_noregion, colour = analysis)) + 
  geom_point() +
  theme_minimal()



```

## Automated runs

```{bash}

sbatch --time 2:00:00 --partition cpu --job-name="pap2" --ntasks 1 --cpus-per-task 6 --mem 256G --wrap="Rscript /scratch/prj/sgdp_nanopore/Projects/prada_jz/src-r/pradaAppPilot2.R" --output "pradaAppPilot2.$(date +%Y%m%d).out.txt"

sbatch --time 2:00:00 --partition cpu --job-name="pap3" --ntasks 1 --cpus-per-task 6 --mem 256G --wrap="Rscript /scratch/prj/sgdp_nanopore/Projects/prada_jz/src-r/pradaAppPilot3.R" --output "pradaAppPilot3.$(date +%Y%m%d).out.txt"

sbatch --time 2:00:00 --partition cpu --job-name="pap4" --ntasks 1 --cpus-per-task 6 --mem 256G --wrap="Rscript /scratch/prj/sgdp_nanopore/Projects/prada_jz/src-r/pradaAppPilot4.R" --output "pradaAppPilot4.$(date +%Y%m%d).out.txt"

sbatch --time 2:00:00 --partition cpu --job-name="pap6" --ntasks 1 --cpus-per-task 6 --mem 256G --wrap="Rscript /scratch/prj/sgdp_nanopore/Projects/prada_jz/src-r/pradaAppPilot6.R" --output "pradaAppPilot6.$(date +%Y%m%d).out.txt"

sbatch --time 2:00:00 --partition cpu --job-name="dshg002" --ntasks 1 --cpus-per-task 6 --mem 256G --wrap="Rscript /scratch/prj/sgdp_nanopore/Projects/prada_jz/src-r/pradaAppDownsampledHg002.R" --output "pradaAppDownsampledHg002.$(date +%Y%m%d).out.txt"

sbatch --time 2:00:00 --partition cpu --job-name="pap8" --ntasks 1 --cpus-per-task 6 --mem 256G --wrap="Rscript /scratch/prj/sgdp_nanopore/Projects/prada_jz/src-r/pradaAppPilot8.R" --output "pradaAppPilot8.$(date +%Y%m%d).out.txt"

sbatch --time 2:00:00 --partition cpu --job-name="pap9" --ntasks 1 --cpus-per-task 6 --mem 256G --wrap="Rscript /scratch/prj/sgdp_nanopore/Projects/prada_jz/src-r/pradaAppPilot9.R" --output "pradaAppPilot9.$(date +%Y%m%d).out.txt"

sbatch --time 2:00:00 --partition cpu --job-name="pap13" --ntasks 1 --cpus-per-task 6 --mem 256G --wrap="Rscript /scratch/prj/sgdp_nanopore/Projects/prada_jz/src-r/pradaAppPilot13.R" --output "pradaAppPilot13.$(date +%Y%m%d).out.txt"

sbatch --time 2:00:00 --partition interruptible_cpu --job-name="plots" --ntasks 1 --cpus-per-task 6 --mem 256G --wrap="Rscript /scratch/prj/sgdp_nanopore/Projects/prada_jz/src-r/unified-plots.R" --output "prada-plots.$(date +%Y%m%d).out.txt"

sbatch --time 8:00:00 --partition interruptible_cpu --job-name="spider" --ntasks 1 --cpus-per-task 6 --mem 256G --wrap="Rscript /scratch/prj/sgdp_nanopore/Projects/prada_jz/src-r/truth-concordance.R" --output "truth-concordance.$(date +%Y%m%d).out.txt"


```


# DB routines


Misc dump and restore

```{bash}

#assuming ssh-tunnel with specified port settngs
pg_dump -h localhost -p 65432 -U postgres -d prada_central_dev -F d -f prada_central_dev_dump -Z 9 -j 6
pg_dump -h localhost -p 65432 -U postgres -d covidcnsdb -F d -f covidcnsdb_dump -Z 9 -j 6
pg_dump -h localhost -p 65432 -U postgres -d phenodb -F d -f phenodb_dump -Z 9 -j 6
pg_dump -h localhost -p 65432 -U postgres -d redash -F d -f redash_dump -Z 9 -j 6

#single transaction restore - same database
pg_restore -h localhost -p 65432 -U postgres -d prada_central_dev -c --if-exists --no-data-for-failed-tables -1 prada_central_dev_dump
#multiple jobs restore - same database
pg_restore -h localhost -p 65432 -U postgres -d prada_central_dev -c --if-exists --no-data-for-failed-tables -j 6 prada_central_dev_dump

#restore to new database
createdb -h localhost -p 65432 -U postgres -W covidcnsdb_restore
pg_restore -h localhost -p 65432 -U postgres -d covidcnsdb_restore -v --no-data-for-failed-tables -j 6 covidcnsdb_dump

#restoring a text format dump - same database (not recommended, because slow)
psql -h localhost -p 65432 -U postgres -d prada_central_old < dump-prada_central-202601191142.sql

```



# QUILT imputation experiments

## Genome chunks definitions 

```{r}

library(STITCH)
library(mspbwt)
library(QUILT)
projectFolderPath<-"/users/k2481717/project/prada_jz"
workFolderPath<-file.path(projectFolderPath,"work","imputation","quilt")

ldat<-c()

for(iChr in 1:22){
  ldat[iChr] <- list(QUILT::quilt_chunk_map(paste0("chr",iChr), paste0("/scratch/prj/ppn_tng/projects/jzphdmove/SHARED/software/QUILT/maps/hg38/CEU-chr",iChr,"-final.b38.txt.gz")))
}
dat <- data.table::rbindlist(ldat,use.names = TRUE,fill = TRUE)
saveRDS(dat,file.path(workFolderPath,"chunks.quilt.Rds"))
#str(dat)


# rare_af_threshold<- 0.001
# subsamples <- "-"
# 
# ifelse(regionStart-buffer<1, samtoolslike <- paste0(chr, ":", 1, "-", regionEnd+buffer), samtoolslike <- paste0(chr, ":", regionStart-buffer, "-", regionEnd+buffer) )
# 
# out <- STITCH::Rcpp_get_hap_info_from_vcf(
#         vcffile = reference_vcf_file,
#         af_cutoff = rare_af_threshold,
#         region = samtoolslike,
#         samples = subsamples
#       )


```

## Reference panel preparation

Creates the slurm commands to run.

```{r}

projectFolderPath<-"/users/k2481717/project/prada_jz"
projectFolderPathLocal<-"/Users/jakz/Documents/work_rstudio/prada"
workFolderPath<-file.path(projectFolderPath,"work","imputation","quilt")


chunks<-readRDS(file.path(projectFolderPathLocal,"chunks.quilt.Rds"))

cf <- data.frame(command=paste0(
  "\n#",1:nrow(chunks),"
  sbatch --time 1:00:00 --partition cpu --job-name=\"c",1:nrow(chunks),"\" --ntasks 1 --cpus-per-task 5 --mem 32G --wrap=\"Rscript ",file.path(projectFolderPath,"src-r","prada-prepare-reference-chunk.R"), " ",1:nrow(chunks),"\" --output \"quiltChunk.",1:nrow(chunks),".$(date +%Y%m%d).out.txt\" 
  
  
  "
)
)

data.table::fwrite(cf,file = file.path(workFolderPath,"prepare-reference-chunk-commands.sh"), append = F, quote = F, sep = "\t", col.names = F, nThread=4, na = "NA") 

```

#Assess imputation quality

```{sh}

bedtools intersect -a /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/quilt/results_01x/quilt.14.1.300000000.vcf.gz -b /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/truth-set/concordance_v2/truth_chr14.vcf.gz

bedtools intersect -a /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/quilt/results_01x/quilt.14.1.300000000.vcf.gz -b /scratch/prj/gwas_sumstats/reference_panel/hc1kgp3.b38.plink/hc1kgp3.b38.eur.jz2024.vcf.gz

bedtools intersect -a /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/output/hg002-01/chr14/hg002-01.chr14.vcf.gz -b /scratch/prj/gwas_sumstats/reference_panel/hc1kgp3.b38.plink/hc1kgp3.b38.eur.jz2024.vcf.gz

bcftools stats /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/reference_panel_final/1000GP_chr14.sites.vcf.gz
#2640944

bedtools intersect -a /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/output/hg002-01/chr14/hg002-01.chr14.vcf.gz -b /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/reference_panel_final/1000GP_chr14.sites.vcf.gz -u | wc -l
#2627602


bedtools intersect -a /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/output/hg002-02/chr14/hg002-02.chr14.vcf.gz -b /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/reference_panel_final/1000GP_chr14.sites.vcf.gz -u | wc -l
#2627602


bedtools intersect -a /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/output/hg002-03/chr14/hg002-03.chr14.vcf.gz -b /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/reference_panel_final/1000GP_chr14.sites.vcf.gz -u | wc -l
#2627602

bedtools intersect -a /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/output/hg002-03/chr14/hg002-03.chr14.vcf.gz -b /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/reference_panel_final/1000GP_chr14.sites.vcf.gz -v | wc -l

bedtools intersect -a /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/reference_panel_final/1000GP_chr14.sites.vcf.gz -b /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/output/hg002-03/chr14/hg002-03.chr14.vcf.gz -v | wc -l
#12935

bedtools intersect -a /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/reference_panel_final/1000GP_chr14.sites.vcf.gz -b /users/k2481717/project/prada_jz/work/pgx/downsampled-bam-runs/imputation/glimpse/output/hg002-02/chr14/hg002-02.chr14.vcf.gz -v | wc -l



```

# hg002 upsampling and downsampling

```{sh}

#merge
sbatch --time 2-00:00:00 --partition cpu --job-name="upsamp" --ntasks 1 --cpus-per-task 32 --mem 128G --wrap="~/project/prada_jz/src-sh/hg002-merge-upsampled.sh" --output "hg002-merge-upsampled.$(date +%Y%m%d).out.txt"

#stats
sbatch --time 12:00:00 --partition cpu --job-name="stats" --ntasks 1 --cpus-per-task 32 --mem 64G --wrap="~/project/prada_jz/src-sh/hg002-downsampling-stats.sh" --output "hg002-downsampling-stats.$(date +%Y%m%d).out.txt"

#downsample
sbatch --time 2-00:00:00 --partition cpu --job-name="downs" --ntasks 1 --cpus-per-task 32 --mem 128G --array=1-5 --wrap="~/project/prada_jz/src-sh/hg002-downsample.sh" --output "hg002-downsample.%a.$(date +%Y%m%d).out.txt"

sbatch --time 2-00:00:00 --partition cpu --job-name="downx" --ntasks 1 --cpus-per-task 32 --mem 128G --wrap="~/project/prada_jz/src-sh/hg002-downsample.sh x" --output "hg002-downsample.x.$(date +%Y%m%d).out.txt"

```

```{r}

library(prada)
library(data.table)

finalBed<-fread("/Users/jakz/Documents/work_rstudio/prada/data/bed/pgx.grch38.padded_100k.bed")

finalBed.compact<-unique(finalBed[,c("V1","V4")])
setDT(finalBed.compact)
finalBed.compact[finalBed[V6=="+",],on=c(V1='V1' , V4='V4'), c('bp1') := list(i.V2)]
finalBed.compact[finalBed[V6=="-",],on=c(V1='V1' , V4='V4'), c('bp2') := list(i.V3)]


colnames(finalBed.compact)<-c("chr_reg","label_reg","bp1_reg","bp2_reg")
#finalBed.compact[,chr_reg:=as.integer(chr_reg)]
unique(finalBed.compact$chr_reg)

pradaO<-PradaClass()
pradaO$connectPradaDatabase(usernameToUse="tng_prada_system", dbnameToUse="prada_central_dev")
dbRegions <- pradaO$pradaApplicationDAO$selectApplicationCoverageRegions(paddingGeneBp = 0, paddingVariantCnvBp = 0, paddingVariantSnpBp = 0, nPrioritisedGene = 1000)
unique(dbRegions$chr_name)

setDT(dbRegions)
dbRegions[finalBed.compact,on=.(chr_name=chr_reg , bp1>bp1_reg, bp2<bp2_reg), c('region') := list(i.label_reg)]

#CYP1A2 from GENCODE: chr15, bp1=74748845, bp2=74756607
#CYP1A2 in BED: chr15, bp1=74638844, bp2=74866607

#CYP2A6 from GENCODE: chr19, bp1=40843541, bp2=40850447
#CYP2B6 (includes CYP2A6) in BED: chr19, bp1=40733540, bp2=41206195

```

